---
title: "Ligada_Example"
author: "Woubie"
date: "17 October 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Biscate.co.mz and the Mozambican labour market

Biscate.co.mz is a platform created by UX, an award-winning Mozambican company that develops locally-relevant, market-driven, and self-sustainable tech-based products and services for high social and economic impact in emerging markets. Biscate.co.mz is a platform that aims to connect blue-collar workers, like e.g. carpenters and painters, to clients that require their services. 


```{r}
setwd("C:/Users/Woubie/Documents/Github/My-Project")
workers <- read.csv("workers_1_data.csv")
#Changing the following variables to factors 
workers$experience_name <- as.factor(workers$experience_name)
workers$education_name <- as.factor(workers$education_name)
workers$district_name <- as.factor(workers$district_name)
workers$province_name <- as.factor(workers$province_name)
workers$profession_name <- as.factor(workers$profession_name)
workers$user_status <- as.factor(workers$user_status)

```
#Structure of Dataset
```{r, echo=FALSE}
str(workers)
```

#Education Level of Workers Registered

```{r, echo=FALSE}
plot(workers$education_name, main="Education Level of Workers", xlab="Education Level",ylab="Number of People")
```

#Experience Level of Workers Registered

```{r, echo=FALSE}
plot(workers$experience_name, main="Years of Work", xlab="Number of Year of Work Experience Level", ylab="Number of People")
```

#Summary of Price Score

```{r, echo=FALSE}
summary(workers$price_score)
```
#Summary of Quality Score 

```{r, echo=FALSE}
summary(workers$quality_score)
```

#Quality vs Price Plot

```{r, echo=FALSE}
plot(workers$quality_score, workers$price_score)
```

