---
title: "Ligada_Example"
author: "Woubie"
date: "17 October 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Biscate.co.mz and the Mozambican labour market

Biscate.co.mz is a platform created by UX, an award-winning Mozambican company that develops locally-relevant, market-driven, and self-sustainable tech-based products and services for high social and economic impact in emerging markets. Biscate.co.mz is a platform that aims to connect blue-collar workers, like e.g. carpenters and painters, to clients that require their services. 

This document presents some preliminary analysis of some initial data gathered through this platform


#Education Level of Workers Registered

```{r worker_1_data, echo=FALSE}
plot(education_name, main="Education Level of Workers", xlab="Education Level",ylab="Number of People")
```

#Experience Level of Workers Registered

```{r worker_1_data, echo=FALSE}
plot(experience_name, main="Years of Work", xlab="Number of Year of Work Experience Level", ylab="Number of People")
```

#Summary of Price Score

```{r worker_1_data, echo=FALSE}
summary(price_score)
```
#Summary of Quality Score 

```{r worker_1_data, echo=FALSE}
summary(quality_score)
```

#Quality vs Price Plot

```{r , echo=FALSE}
plot(quality_score, price_score)
```

